Measurement Clusterization in Bayesian D-optimal Designs in Infinite Dimensions

### 2024-12-08 latex/intro.tex
BA minor revision

@@

%% Gaussian
One potential cause of clusterization is our choice of prior. Gaussian
priors, coupled with a Gaussian likelihood and a linear forward
problem give rise to a closed form solution for the posterior via
conjugacy. As we show in Section \ref{subsec:lemma_sims}, such
assumptions generically give rise to clusterization. While an
assumption of a Gaussian likelihood is standard, and rooted in the
central limit theorem, an assumption of Gaussian prior is merely a
matter of convenience. Therefore, we advise any practitioner who
encounters clusterization to replace their Gaussian priors with
non-Gaussian priors instead \cite{hosseini2017, hosseini2019}.

>>>>

As another example illustrating the differences between replication
and clusterization, consider an experiment involving a chemical
reaction at different temperatures. An investigator may choose to
\emph{replicate} the experiment at $10^\circ C$ and $30^\circ
C$. Within a single replication, the investigator may also choose to
take measurements at different times. If the investigator chooses to
take two measurements at the same time (within a single replication),
then the investigator has utilized a \emph{clustered} design. While
replication is intuitively sensible for this chemical experiment,
clusterization is not.

@@

%% Gaussian
One potential cause of clusterization is our choice of prior. Gaussian
priors, coupled with a Gaussian likelihood and a linear forward
problem give rise to a closed form solution for the posterior via
conjugacy. As we show in Section \ref{subsec:lemma_sims}, such
assumptions generically give rise to clusterization. While an
assumption of independent Gaussian noise (likelihood) is standard, and
rooted in the central limit theorem, an assumption of Gaussian prior
is merely a matter of convenience. Therefore, we advise practitioners
encountering clusterization to replace Gaussian priors with
non-Gaussian ones \cite{hosseini2017, hosseini2019}, as these are not
only more realistic but also expected to mitigate clusterization.
